## **GRI**

```{r gri_setup, echo = FALSE}
classes <- andiacare::allowedDiabetesClassifiers()$GRI$Classes(meta = TRUE)
griClassesColors <- classes$Color
names(griClassesColors) <- classes$Class
classesAreas <- as.data.frame(do.call(rbind,lapply(rev(seq(nrow(classes))),
  function(i){
    Hypo <- c(classes$HypoCmin[i],classes$HypoCmax[i])
    Hyper <- c(classes$HyperCmin[i],classes$HyperCmax[i])
    cls <- classes$Class[i]
    corners <- data.frame(
                  Hyper = c(0,      0,      Hyper[2],Hyper[1]),
                  Hypo  = c(Hypo[1],Hypo[2],0,       0))
    corners$Group <- rep(paste0('GRI',cls),4)
    N <- nrow(corners)
    colnames(corners) <- c('Hyper','Hypo','Group')
    return(cbind(data.frame(Class = rep(cls,N),
                            Color = rep(classes$Color[i],N)),
                 corners))
})))
cohort$GRI <- factor(cohort$GRI, levels = classes$Class)
```

The algorithm _glycemia Risk Index_ (GRI) it's an [external algorithm](https://journals.sagepub.com/doi/10.1177/19322968221085273) and applies a triage classification using colors. It's based on an index calculated using Time in Range (TIR), Bellow (Low) and Above (High), including severe hyperglycemia events (VHigh; >250 mg/dL) and sever hipoglycemia events (VLow; <54 mg/dL).

If necessary info is not available, patient can be classified as _Unclassified_. It could be caused by NAs presence.

Formulas used by this algorithm are:

$$HypoC = VLow + (0.8 * Low) $$
$$HyperC = VHigh + (0.5 * Low)$$
$$GRI = (3 * HypoC) + (1.6 * HyperC)$$


A bidimensional representation of this algorithm classifier is:

```{r gri_classes, echo = FALSE}
# Plot area by are to handle overlapping
ppArea <- ggplot2::ggplot()
invisible(sapply(unique(classesAreas$Class),function(cl){
  ppArea <<- ppArea + 
        ggplot2::geom_polygon(data = classesAreas[classesAreas$Class == cl,],
                              mapping = ggplot2::aes(x = Hyper, y = Hypo,
                                 fill = Class, group = Group)) 
}))
ppArea <- ppArea + 
          ggplot2::scale_fill_manual(name = 'Class',
                                    values = griClassesColors,
                                    labels = names(griClassesColors)) +
          ggplot2::xlim(0,65) + 
          ggplot2::ylim(0,35)

plot(ppArea)
```

### **Cohort results**

Applying the algorithm to `r nrow(cohort)` cohort, we obtain the following distribution:

```{r gri_plotCohortResults, echo = FALSE} 
aux <- as.data.frame(table(cohort$GRI))
N <- nrow(cohort)
colnames(aux) <- c("label","value")
aux$color <- as.vector(sapply(seq(nrow(aux)),function(i){
  return(griClassesColors[which(names(griClassesColors) == aux$label[i])])
}))
aux$perclabels <- paste(round(aux$value/sum(aux$value) * 100, 2), "%")
aux$Class <- paste0(aux$label, " (", aux$value, ")")


classes$Label <- sapply(seq(nrow(classes)),function(i){
  count <- aux$value[which(aux$label == classes$Class[i])]
  if(length(count) == 0) count = 0
  return(paste0(classes$Class[i]," (",
                count,")"))
})

toinclude <- c('HypoglycemiaC','HyperglycemiaC',"GRI","GRIVal")
if(flags$Birthdate) toinclude <- c(toinclude, "AgeRange")
if(flags$Source) toinclude <- c(toinclude, "Source")

auxpats <- cohort[,toinclude]
auxpats$ClassLabel <- sapply(auxpats$GRI,function(cl){
  return(classes$Label[which(classes$Class == cl)[1]])
})

# levels(auxpats$ClassLabel) <- classes$Label
names(griClassesColors) <- classes$Label
auxpats$ClassLabel <- factor(auxpats$ClassLabel, levels = classes$Label) 
ppScatClasses <- ggplot2::ggplot(auxpats, 
                    ggplot2::aes(x = HyperglycemiaC, 
                      y = HypoglycemiaC, 
                      colour = ClassLabel,
                      text = paste("Age:", AgeRange, "\nGRIVal", GRIVal))) +
       ggplot2::geom_point(alpha=0.4, na.rm = TRUE) +
       ggplot2::scale_color_manual(name = "Class",
                                values = griClassesColors) +
       ggplot2::xlim(0,65) +
       ggplot2::ylim(0,35) 
# Pieplot
# rAmCharts::amPie(data = aux, inner_radius = 50, depth = 15)
aux <- aux[aux$value > 0,]
gripie <- ggplot2::ggplot(aux, ggplot2::aes(x = "", y = value, fill = Class)) +
    ggplot2::geom_bar(stat = "identity", width = 1) +
    ggplot2::coord_polar("y", start = 0) +
    ggplot2::xlab("") +
    ggplot2::ylab("") +
    ggplot2::scale_fill_manual(values = griClassesColors) +
    ggplot2::geom_text(aes(label = perclabels),
            position = ggplot2::position_stack(vjust = 0.5)) +
    ggplot2::theme_void()
plot(gripie)


# Scatter plot
plotly::ggplotly(ppScatClasses) %>% 
  plotly::layout(xaxis = list(fixedrange = TRUE), 
                yaxis = list(fixedrange = TRUE))

# Store info
graphlist_algs$GRI <- list(ppScatClasses,
        gridExtra::tableGrob(andiacare:::tableFromCharVector(cohort$GRI)))
```

### **Breakdown of results**

Same results **splitted by final classification** are:

```{r gri_spllitedResByClass, echo = FALSE}
ppSCSplitted <- ppScatClasses + 
        ggplot2::facet_wrap(~ ClassLabel) + 
        ggplot2::theme(legend.position = "none")
plot(ppSCSplitted)
```

```{r gri_classAndAge, echo = FALSE}
out <- ""
if(flags$Birthdate){
  body <- "And **splitted by age**:"
  chunkSplitAge <- '
    ppSCSplittedAge <- ppScatClasses + 
            ggplot2::facet_wrap(~ AgeRange) + 
            ggplot2::theme(legend.position = "none")
    plot(ppSCSplittedAge)
  '
  out <- paste("\n",
    body,
    "\n",
    chunks(chunkSplitAge,"and_classAndAgePlot, echo = FALSE"),
    sep = "\n")
}
```

`r paste(knitr::knit(text = out), collapse = '\n')`