## **ATTD19 consensus targets**

```{r attd_setup, echo = FALSE}
meetT_patients <- list()
invisible(lapply(possible_targets,function(txr){
    if(txr %in% colnames(cohort)){
        meetT_patients[[strsplit(txr,"_")[[1]][2]]] <<- which(cohort[, txr])
    }
}))

indxMeet <- Reduce(intersect, meetT_patients)
indxMeetNS <- Reduce(intersect, meetT_patients[c("TIR","TAR","TBR")])
```

At this section, we focus on ATTD 2019 consensus where some targets were fixed. Those targets, which are applied here, are:

- Time In Range (TIR) > 70%
- Time Bellow Range (TBR) < 4%
- Time Above Range (TAR) < 25%
- Time Bellow Range Severe (TBRS) < 1%
- Time Above Range Severe (TARS) < 5%

Checking our patients we obtain following distribution:
```{r attd_venn, echo = FALSE}
vennColors <- rangesColors[names(meetT_patients)]

silent <- futile.logger::flog.threshold(futile.logger::ERROR,
                                        name = "VennDiagramLogger")
vd <- VennDiagram::venn.diagram(meetT_patients,
        fill = vennColors,
        alpha = rep(0.5, length(vennColors)),
        print.mode = c("raw", "percent"),
        filename = NULL)
grid::grid.newpage()
grid::grid.draw(vd)
```

And a correlation study for patients which reach **all targets (`r length(indxMeet)`)**, not severe targets and all which not meet all the targets:
```{r attd_corr, echo = FALSE, warning=FALSE}
if(length(indxMeet) > 2) gridExtra::grid.arrange(
    andiacare::corrChart(cohort[indxMeet, ]),
    top = grid::textGrob("Meet all targets",
        gp = grid::gpar(fontsize = 20, font = 3)))
if(length(indxMeetNS) > 2) gridExtra::grid.arrange(
    andiacare::corrChart(cohort[indxMeetNS, ]),
    top = grid::textGrob("Meet all (not severe) targets",
        gp = grid::gpar(fontsize = 20, font = 3)))
if(nrow(cohort) - length(indxMeet) > 2){
    auxIndx <- setdiff(seq(nrow(cohort)), indxMeet)
    gridExtra::grid.arrange(andiacare::corrChart(cohort[auxIndx, ]),
        top = grid::textGrob("Not meet all targets",
            gp = grid::gpar(fontsize = 20, font = 3)))

}
```


Now, a distributions for cohort which meet all main targets (TIR, TAR and TBR) and which not is:
```{r attd_tables, echo = FALSE, warning=FALSE}
tableMeet <- andiacare::statsTable(cohort[indxMeet,],
                title = "Meet all targets")
tableMeetNS <- andiacare::statsTable(cohort[indxMeetNS,],
                title = "Meet all (not severe) targets")
tableNotMeet <- andiacare::statsTable(cohort[-indxMeet,],
                title = "Not meet all targets")

# Render
gridExtra::grid.arrange(tableMeet, tableMeetNS, ncol = 2)
gridExtra::grid.arrange(tableNotMeet)
```

```{r attd_age_setup, echo = FALSE}
cout <- "\n\n"

if(flags$Birthdate){
    cout <- paste0(knitr::knit_expand("partial_attd_age.Rmd"),
                    "\n\n")
}
```

`r paste(c(knitr::knit(text = paste(cout,collapse = "\n")),"\n"),collapse = "\n")`
