## **Andiacare**

```{r and_setup, echo = FALSE}
classes <- andiacare::allowedDiabetesClassifiers()$Andiacare$Classes(meta = TRUE)
andClassesColors <- classes$Color
names(andClassesColors) <- classes$Class
cohort$Andiacare <- factor(cohort$Andiacare, levels = classes$Class)
```

Andiacare algorithm is our own algorithm and applies a triage over patients classifing them using colors. It algorithm is based on Time in Range (TIR) and Time Bellowe Range (TBR) info.

If necessary info is not available, patient can be classified as _Not Allowed_; and patients with strange artifacts will be flagged as _Unclassified_. It could be caused by NAs presence.

Our algorithm uses info about time in range (TIR), bellow range (TBR) and above range (TAR) using the following thresholds:

* **Green:** (TIR > 70%) and (TBR < 4%) and (TAR < 25%) 
* **Yellow:** (40% < TIR <= 70% ) or (4% <= TBR < 11%) or (25% <= TAR < 50%) 
* **Orange:** (25% < TIR <= 40% ) or (11% <= TBR < 20%) or (50% <= TAR < 75%) 
* **Red:** (TIR <= 25%) or (TBR >= 20%) or (TAR >= 75%) 

**Important::** Green class has been designed to match with some of ATTD19 consensus targets (not all). Rest of thresholds are a linear distribution of this targets along possible dimension. Authros know that and want to adjust those thresholds to real ones making a study of this variables with real future problems along DM1 patients.

### **Cohort results**

Applying the algorithm to `r nrow(cohort)` patients, we obtain the following distribution:

```{r and_plotCohortResults, echo = FALSE, warning=FALSE}    
# Donutplot
aux <- as.data.frame(table(cohort$Andiacare))
N <- nrow(cohort)
colnames(aux) <- c("label","value")
aux$color <- as.vector(sapply(seq(nrow(aux)),function(i){
  return(andClassesColors[which(names(andClassesColors) == aux$label[i])])
}))
aux$perclabels <- paste(round(aux$value/sum(aux$value) * 100, 2), "%")
aux$Class <- paste0(aux$label, " (", aux$value, ")")

classes$Label <- sapply(seq(nrow(classes)),function(i){
  count <- aux$value[which(aux$label == classes$Class[i])]
  if(length(count) == 0) count = 0
  return(paste0(classes$Class[i]," (",
                count,")"))
})


toinclude <- c("TIR", "TBR", "TAR", "Andiacare")
if(flags$Birthdate) toinclude <- c(toinclude, "AgeRange")
if(flags$Source) toinclude <- c(toinclude, "Source")

auxpats <- cohort[,toinclude]
auxpats$ClassLabel <- sapply(auxpats$Andiacare,function(cl){
  return(classes$Label[which(classes$Class == cl)[1]])
})

names(andClassesColors) <- classes$Label
auxpats$ClassLabel <- factor(auxpats$ClassLabel, levels = classes$Label)



# -----------------
# Pieplot
# -----------------
aux <- aux[aux$value > 0,]
andpie <- ggplot2::ggplot(aux, ggplot2::aes(x = "", y = value, fill = Class)) +
    ggplot2::geom_bar(stat = "identity", width = 1) +
    ggplot2::coord_polar("y", start = 0) +
    ggplot2::xlab("") +
    ggplot2::ylab("") +
    ggplot2::scale_fill_manual(values = andClassesColors) +
    ggplot2::geom_text(aes(label = perclabels),
            position = ggplot2::position_stack(vjust = 0.7)) +
    ggplot2::theme_void()
plot(andpie)

# -----------------
# Scatter plot tridimensional
# -----------------
ppScat3D <- plotly::plot_ly(auxpats,
            x = ~TIR,
            y = ~TAR,
            z = ~TBR,
            color = ~ClassLabel,
            colors = andClassesColors)
ppScat3D <- ppScat3D %>% plotly::add_markers()
ppScat3D <- ppScat3D %>% plotly::layout(scene = list(
            xaxis = list(title = "Time In Range (%)"),
            yaxis = list(title = "Time Above Range (%)"),
            zaxis = list(title = "Time Bellow Range (%)")
))
ppScat3D


# -----------------
# Scatter plot bidimensional
# -----------------
ppScatClasses <- ggplot2::ggplot(auxpats,
                    ggplot2::aes(x = TIR, y = TBR, colour = ClassLabel)) +
    ggplot2::geom_point(alpha=0.4, na.rm = TRUE,
            ggplot2::aes(text=paste("Age:",AgeRange))) +
    ggplot2::scale_color_manual(name = "Class",
                                values = andClassesColors) +
    ggplot2::xlim(0,100) +
    ggplot2::ylim(0,100) 


# Store info
graphlist_algs$Andiacare <- list(ppScatClasses,
        gridExtra::tableGrob(andiacare:::tableFromCharVector(cohort$Andiacare)))
```

### **Breakdown of results**

Same results **splitted by final classification** are:

```{r and_spllitedResByClass, echo = FALSE}
ppSCSplitted <- ppScatClasses + 
        ggplot2::facet_wrap(~ ClassLabel) +
        ggplot2::theme(legend.position = "none")
plot(ppSCSplitted)
```

```{r and_classAndage, echo = FALSE}
out <- ""
if(flags$Birthdate){
  body <- "And **splitted by age**:"
  chunkSplitAge <- '
    ppSCSplittedAge <- ppScatClasses + 
            ggplot2::facet_wrap(~ AgeRange) + 
            ggplot2::theme(legend.position = "none")
    plot(ppSCSplittedAge)
  '
  out <- paste("\n",
    body,
    "\n",
    chunks(chunkSplitAge,"and_classAndAgePlot, echo = FALSE"),
    sep = "\n")
}
```

`r paste(knitr::knit(text = out), collapse = '\n')`