```{r setup_att_byAge, echo = FALSE}
targets = c("TIR", "TBR", "TBRS", "TAR", "TARS", "GMI", "MeanReads",
                "SourceSize")
targets <- targets[targets %in% colnames(cohort)]

# Check problematic variables (possible to be all the same)
if("SourceSize" %in% targets){
    if(length(unique(cohort$SourceSize)) <= 1){
        targets <- targets[targets != "SourceSize"]
    }
}

# Check possible Age errors
thr <- 2
auxAges <- table(cohort$AgeRange)
toRemoveBool <- rep(FALSE, nrow(cohort))
if (any(auxAges <= thr & auxAges > 0)) {
    toRemoveAges <- names(auxAges[auxAges <= thr])
    toRemoveBool <- cohort$AgeRange %in% toRemoveAges
}
```

Finally, cohort stats stratified by their age range:
```{r attd_table_byAge, echo = FALSE}
age_ranges <- sort(unique(cohort$AgeRange))
meansMatrix <- matrix(ncol = 0, nrow = 0)

ageATTDTables <- lapply(age_ranges, function(rnge){
    auxCohort <- cohort[cohort$AgeRange == rnge, ]
    rawTable <- andiacare::statsTable(auxCohort, decimals = 2)
    renderedTable <- andiacare::statsTable(auxCohort,
                title = as.character(rnge),
                boolTargets = possible_targets)
    # Export
    info <- paste(rawTable[, "mean"], rawTable[, "sd"], sep = "±")
    if(ncol(meansMatrix) == 0){
        meansMatrix <<- matrix(info, ncol = 1)
        rownames(meansMatrix) <<- rownames(rawTable)
    }else{
        meansMatrix <<- cbind(meansMatrix, info)
    }
    return(renderedTable)
})
colnames(meansMatrix) <- age_ranges
gridExtra::grid.arrange(gridExtra::tableGrob(meansMatrix))

invisible(lapply(seq(1, length(ageATTDTables), 2), function(i){ # Plot in pairs
    if(length(ageATTDTables) >= i+1){
        gridExtra::grid.arrange(ageATTDTables[[i]], ageATTDTables[[i+1]],
            ncol = 2)
    }else{
        gridExtra::grid.arrange(ageATTDTables[[i]])
    }
}))
```

In order to study significant differences between age ranges, a statistical test is used. We assume that sets have different sizes and variances homogeneity can have bias. For that reason the **Games-Howell test**. Interpretation instructions are [here](https://rpkgs.datanovia.com/rstatix/reference/games_howell_test.html). `r ifelse(any(toRemoveBool), paste0("Also a pull of (",sum(toRemoveBool),") patients have been removed because they are unique in their age range. "), "")`A table with all results is shown:
```{r attd_age_differences, echo = FALSE, warning=FALSE}
includeIndx <- seq(nrow(cohort))
if(any(toRemoveBool)){
    includeIndx <- includeIndx[!toRemoveBool]
}
statTestsByAge <- as.data.frame(do.call(rbind, lapply(targets, function(trg){
    rstatix::games_howell_test(cohort[includeIndx,c(trg, "AgeRange")],
            formula(paste0(trg, " ~ AgeRange")),
            conf.level = 0.95,
            detailed = TRUE)
})))

statTestsByAge$.y. <- as.factor(statTestsByAge$.y.)
statTestsByAge$group1 <- as.factor(statTestsByAge$group1)
statTestsByAge$group2 <- as.factor(statTestsByAge$group2)
statTestsByAge$p.adj.signif <- as.factor(statTestsByAge$p.adj.signif)
DT::datatable(statTestsByAge, filter = 'top', options = list(pageLength = 10,
    autoWidth = TRUE))
```